
% Acknowledgments File


\begin{center}

\end{center}
\begin{center}

{\bf\fontsize{14pt}{14.5pt}\selectfont \uppercase{Acknowledgements}}\\\vspace{1cm}
\end{center}

\addcontentsline{toc}{chapter}{Acknowledgements} % (Optional)





I would like to personally express my gratitude to all participating parties who have made this project possible. Firstly, to Dr. McCormick, my thesis advisor and introductory proofs class professor. My success in upper-division classes like real analysis and abstract algebra can be traced back to your lectures. Thank you for dedicating your time and effort to guiding me through the process of writing my very first thesis, something that I never saw myself doing. I am grateful for your patience and feedback in reviewing all the pages of each document and providing advice in writing the Mathematica code to collect the necessary data needed for this thesis.

Secondly, thank you to my parents and grandmother for being an inspiration to go beyond the limits of my own potential. Without their words of encouragement and belief in my abilities, I would not have been able to finish or even continue the thesis during the many times of struggling with getting things right. Thank you for giving me reassurance during all the times I got overwhelmed with all the calculations and lines of code.

Thirdly, I would like to thank Dr. Murray for not only being my Honors Calculus III professor but for also being a huge inspiration and mentor in the field of mathematics. It is your enthusiastic energy and amazing lectures that have fueled my thirst for knowledge from basic mathematics all the way to introductory ring theory. Thank you for your time talking to me even outside of office hours, and I hope to learn so much more about the curiosities that mathematics has to offer.

